Although this is not the official name for this test system, it was first proposed by Gershgorin, Harlim, and Majda in \cite{Gershgorin10}. Specifically, the exactly solvable test model is

\begin{align}
	\frac{d\,u\left( t \right)}{dt} &= \left( -\gamma\left( t \right) + i\,\omega \right)\,u\left( t \right) + b\left( t \right) + f\left( t \right) + \sigma\,\dot{W}\left( t \right), \label{eqn:diff_b}\\
	\frac{d\,b\left( t \right)}{dt} &= \left( -\gamma_{b} + i\,\omega_{b} \right)\,\left( b\left( t \right) + \widehat{b} \right) + \sigma_{b}\,\dot{W}_{b}\left( t \right), \label{eqn:diff_gamma}\\
	\frac{d\,\gamma\left( t \right)}{dt} &= -d_{\gamma}\,\left( \gamma\left( t \right) + \widehat{\gamma} \right) + \sigma_{\gamma}\,\dot{W}_{\gamma}\left( t \right), \label{eqn:diff_u}
\end{align}

where $u\left( t \right)$ and $b\left( t \right)$ are complex-valued and $\gamma\left( t \right)$ is real-valued. The terms $b\left( t \right)$ and $\gamma\left( t \right)$ represent additive and multiplicative bias corrections terms. Also, $\omega$ is the oscillation frequency of $u\left( t \right)$, $f\left( t \right)$ is external forcing, and $\sigma$ characterizes the strength of the white noise forcing $\dot{W}\left( t \right)$. The parameters $\gamma_{b}$ and $d_{\gamma}$ represent the damping and parameters $\sigma_{b}$ and $\sigma_{\gamma}$ represent the strength of the white noise forcing of the additive and multiplicative bias correction terms, respectively. The parameters $\widehat{b}$ and $\widehat{\gamma}$ are the stationary mean bias correction values of $b\left( t \right)$ and $\gamma\left( t \right)$, correspondingly, and $\omega_{b}$ is the frequency of the additive noise. Note that the white noise $\dot{W}_{\gamma}\left( t \right)$ is real-valued while the white noises $\dot{W}\left( t \right)$ and $\dot{W}_{b}\left( t \right)$ are complex-valueds and their real and imaginary parts are independent real-valued white noises.

In \cite{Gershgorin10}, they consider an oscillatory external forcing

\begin{align}
	f\left( t \right) &= A_{f}\,e^{i\,\omega_{f}\,t}
\end{align}

with $A_f$ the strength of the external forcing and $\omega_f$ its frequency. We utilize a forcing of this form in the code.

The pathwise solutions and exact statistics (up to second order) are included in Appendices~\ref{app:pathwise_solns} and \ref{app:exact_stats}, respectively.

