This code is a test example for the multi-model forecast Kalman filter, as initially formulated in November 2020. In particular, we assume linear, Gaussian models and utilize some linear combination of our models to create a psuedo-truth signal for each model that that model observes. The purpose of this code, at least initially, is to be able to run the Gershgorin-Majda 2010 system, as well as the additive and multiplicative models.

This document is inteded to be supplemental documentation for the \texttt{README.md} files included throughout the code repository.

\subsection{The Gershgorin-Majda 2010 System}

Although this is not the official name for this test system, it was first proposed by Gershgorin and Majda in \cite{Gershgorin10}. Specifically, the exactly solvable test model is

\begin{align}
	\frac{d\,u\left( t \right)}{dt} &= \left( -\gamma\left( t \right) + i\,\omega \right)\,u\left( t \right) + b\left( t \right) + f\left( t \right) + \sigma\,\dot{W}\left( t \right), \\
	\frac{d\,b\left( t \right)}{dt} &= \left( -\gamma_{b} + i\,\omega_{b} \right)\,\left( b\left( t \right) + \widehat{b} \right) + \sigma_{b}\,\dot{W}_{b}\left( t \right),\\
	\frac{d\,\gamma\left( t \right)}{dt} &= -d_{\gamma}\,\left( \gamma\left( t \right) + \widehat{\gamma} \right) + \sigma_{\gamma}\,\dot{W}_{\gamma}\left( t \right),
\end{align}

where $u\left( t \right)$ and $b\left( t \right)$ are complex-valued and $\gamma\left( t \right)$ is real-valued. The terms $b\left( t \right)$ and $\gamma\left( t \right)$ represent additive and multiplicative bias corrections terms. Also, $\omega$ is the oscillation frequency of $u\left( t \right)$, $f\left( t \right)$ is external forcing, and $\sigma$ characterizes the strength of the white noise forcing $\dot{W}\left( t \right)$. The parameters $\gamma_{b}$ and $d_{\gamma}$ represent the damping and parameters $\sigma_{b}$ and $\sigma_{\gamma}$ represent the strength of the white noise forcing of the additive and multiplicative bias correction terms, respectively. The parameters $\widehat{b}$ and $\widehat{\gamma}$ are the stationary mean bias correction values of $b\left( t \right)$ and $\gamma\left( t \right)$, correspondingly, and $\omega_{b}$ is the frequency of the additive noise. Note that the white noise $\dot{W}_{\gamma}\left( t \right)$ is real-valued while the white noises $\dot{W}\left( t \right)$ and $\dot{W}_{b}\left( t \right)$ are complex-valueds and their real and imaginary parts are independent real-valued white noises.

In \cite{Gershgorin10}, they consider an oscillatory external forcing

\begin{align}
	f\left( t \right) &= A_{f}\,e^{i\,\omega_{f}\,t}
\end{align}

with $A_f$ the strength og the external forcing and $\omega_f$ its frequency. For the purpose of testing some parameter estimation techniques, Gershgorin and Majda considered an additive model of the original Gershgorin-Majda 2010 system where there is only additive bias correction

\begin{align}
	\frac{d\,u\left( t \right)}{dt} &= \left( -\overline{d} + i\,\omega \right)\,u\left( t \right) + b\left( t \right) + f\left( t \right) + \sigma\,\dot{W}\left( t \right), \\
	\frac{d\,b\left( t \right)}{dt} &= \left( -\gamma_{b} + i\,\omega_{b} \right)\,\left( b\left( t \right) + \widehat{b} \right) + \sigma_{b}\,\dot{W}_{b}\left( t \right),
\end{align}

where $\overline{d}$ is the mean value of the damping, as well as a multiplicative model where there is only multiplicative bias correction

\begin{align}
	\frac{d\,u\left( t \right)}{dt} &= \left( -\gamma\left( t \right) + i\,\omega \right)\,u\left( t \right) + f\left( t \right) + \sigma\,\dot{W}\left( t \right), \\
	\frac{d\,\gamma\left( t \right)}{dt} &= -d_{\gamma}\,\left( \gamma\left( t \right) + \widehat{\gamma} \right) + \sigma_{\gamma}\,\dot{W}_{\gamma}\left( t \right).
\end{align}
